{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-22 paper/paper.tex
added a defintion of jun

>>>>

With this definition of $tregion$ in mind, it is easy to define the junction points.

\begin{definition}{jun}
The junction points are computed by a function $jun: \mathcal{P} \rightarrow \mathcal{P}$. It is defined
on all junction points $[c]^n$ in the source program and its domain looks like $max \{i\ |\ i \in tregion(n)\} + 1$.
\end{definition}

Intuitively a junction point according to this definition is the point that follows on the last instruction
that is affected by the branching instruction.
